It is important for the user to perform a risk assessment when using this product. Refer to the UR5 user manual for additional detailed specifications and requirements of the product's hardware. 

\subsection{Workspace Assessment}
\subsubsection{Description}
The UR5 must be used in a workspace within a radius of 850mm of the base. For all required functions, the tools and and attachments can only be used within this space. 

The UR5 has a maximum payload of 11 pounds so we must keep that in mind when assigning tasks.

The griddle work area must be clear and all attached equipment (namely the tool contacting the griddle) must be able to tolerate high temperature heat (upwards of 400°F)
\subsubsection{Priority}
Medium

\subsection{Tool and Attachment Bindings}
\subsubsection{Description}
Any tool or removable attachment secured to the mount of the UR5 must go through a safety check to ensure that the tool is secured and will not move within the mount while in use. This is to ensure the integrity and safety of the system. The tool and all attached components must also be able to handle the high temperatures mentioned above.
\subsubsection{Priority}
High


\subsection{Ability to Prepare a Grill Cheese Sandwich}
\subsubsection{Description}
The \productname{} should be able to prepare an edible grill cheese sandwich to completion. 
\subsubsection{Standards}
- The bread must be properly toasted. 
- The finished sandwich must be properly placed on the "finished" by the UR5.   
\subsubsection{Priority}
High
